Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-20 revisionMemo/rev1.tex
cites

		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance.  Though we understand these goals are not always central to every political scientists aim, we do believe they relate closely to the field of IR (as demonstrated by the studies we replicate) and a growing interest in forecasting and machine learning in Political Science. (CITE?) [add reference to DGM JOP in which AME beat random forest]

@@

		\item Finally, we understand these goals are not always central political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in \citet{people}.

>>>>

		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance. 

@@

		\item Finally, we understand these goals are not always central political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in Gleditsch and Ward 2013; Grimmer 2015; Muchlinski et al. 2016; Colaresi and Mahmood 2017; Mueller and Rauh 2018. 
